Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2017-12-19 eurocg/paper.tex
start of preliminaries, added macros for ped and maxsped

@@

\section{Preliminaries}

Fabian

\begin{itemize}
	\item basic definitions and notation
	\item segment intersection graph
	\item alle planaren Graphen können auftreten (insbes. Bäume und Kakteen)
\end{itemize}

Input: $k$-plane graph drawing $\Gamma$ of a graph $G$ with edge set $S={s_1, \dots, s_m}$ (set of segments)

Intersection graph $C=(V,E)$ with $V=S$ and edges if two segments intersect

Consider maximum degree of $C$ -- here mostly 3.

>>>>

\newcommand{\ped}{\ensuremath{\textsc{PED}}\xspace}
\newcommand{\maxsped}{\ensuremath{\textsc{MaxSped}}\xspace}

@@

\section{Preliminaries}
%\begin{itemize}
%	\item basic definitions and notation
%	\item segment intersection graph
%	\item alle planaren Graphen können auftreten (insbes. Bäume und Kakteen)
%\end{itemize}
%Input: $k$-plane graph drawing $\Gamma$ of a graph $G$ with edge set $S={s_1, \dots, s_m}$ (set of segments)
%Intersection graph $C=(V,E)$ with $V=S$ and edges if two segments intersect 
%Consider maximum degree of $C$ -- here mostly 3.

Let $ G $ be a \emph{simple graph} with edge set $ S = \{s_1,\dots,s_m\}$ and $ \Gamma $ a straight line drawing of $ G $ in the plane. We call $ \Gamma $ \emph{$ k $-plane} if every edge $ s_i \in S $ is crossed by at most $ k $ other edges from $ S $ in $ \Gamma $. The \emph{intersection graph} $ C = (V,E) $ of $ \Gamma $ is the graph containing one vertex in $ V $ for every $ s_i \in S $ and an edge $ uv \in E $ between vertices $ u,v \in V $ whenever the to $ u $ and $ v $ corresponding edges $ s_i, s_j \in S $ intersect in $ \Gamma $. Observe that the intersection graph $ C $ of a $ k $-plane drawing $ \Gamma $ has maximum degree $ k $. Its known that every planar graph is also representable as intersection graph of line segments \cite{chalopin2009every}.

\fabian{This part has to be adapted once the intro is fixed}
We define a \emph{partial edge drawing} \ped $ \Gamma' $ of $ G $ as a drawing using the same embedding as $ \Gamma $, but edges are drawn as \emph{stubs}, i.e., we do not depict an edge $ s_i \in S $ by a line segment connecting the two vertices, but remove the middle part of the edges such that no two stubs intersect in $ \Gamma' $. We call a \ped $ \Gamma' $ \emph{symmetric} if for one edge $ s_is_j \in S $ its stub have equal lengths in $ \Gamma' $. Finally we define \maxsped as a symmetric \ped $ \gamma' $ of $ G $ where the sum of the lengths of the stubs is maximized.
